Tables

### 2020-11-12 manuscript/manuscript.Rmd
Edits: major change

---
title: "Ecosystem size and complexity dictate riverine biodiversity"
author:
- name: Akira Terui
  email: hanabi0111@gmail.com
  affiliation: Department of Biology, University of North Carolina at Greensboro
  footnote: Corresponding Author
- name: Seoghyun Kim
  email: s_kim53@uncg.edu
  affiliation: Department of Biology, University of North Carolina at Greensboro
address:
- address: Department of Biology, Greensboro, NC
output: html_notebook
bibliography: reference.bib
csl: nature.csl
abstract: |
  This is the abstract.
  It consists of two paragraphs.
---

>>>>

---
title: "Ecosystem size and complexity dictate riverine biodiversity"
author:
- name: Akira Terui
  email: hanabi0111@gmail.com
  affiliation: Department of Biology, University of North Carolina at Greensboro
  footnote: Corresponding Author
- name: Seoghyun Kim
  email: s_kim53@uncg.edu
  affiliation: Department of Biology, University of North Carolina at Greensboro
- name: Christy Dolph
  email: XXX
  affiliation: XXX
output: html_notebook
bibliography: reference.bib
csl: nature.csl
abstract: |
  This is the abstract.
  It consists of two paragraphs.
---

### 2020-11-12 manuscript/table.Rmd
Edits: major change

---
title: "R Notebook"
output: html_notebook
---
```{r setup, include=FALSE}
# setup -------------------------------------------------------------------

  rm(list = ls(all.names = TRUE))
  pacman::p_load(tidyverse, MuMIn, gt)
  options(na.action = "na.fail")
  setwd(here::here("empirical"))

# read data ---------------------------------------------------------------

  dat_hkd <- read_csv("data_out/data_hkd.csv") %>% mutate(region = "hokkaido")
  dat_mw <- read_csv("data_out/data_mw.csv") %>% mutate(region = "midwest")
  dat <- bind_rows(dat_hkd, dat_mw) %>% 
    rename(gamma = Estimator,
           gamma_lower = '95% Lower',
           gamma_upper = '95% Upper') %>% 
    mutate(beta = gamma/mu_alpha,
           beta_lower = gamma_lower/mu_alpha,
           beta_upper = gamma_upper/mu_alpha,
           logit_forest = log(frac_forest) - log(1 - frac_forest))

  ## gamma
  fit <- lm(log(gamma) ~ log(area)*region + log(p_branch)*region + scale(mean_temp) + scale(mean_ppt) + scale(logit_forest), dat)
  m <- dredge(fit, rank = "AIC")
  re <- model.avg(object = m, subset = delta < 2)
  x <- summary(re)
  knitr::kable(x$coefmat.subset)
  predict(re$call)
```

>>>>

---
title: "Tables"
output:
  pdf_document: default
---

```{r setup, include=FALSE}

  knitr::opts_knit$set(root.dir = here::here("empirical"))

```

```{r, echo = FALSE, message=FALSE, results='asis'}

source(normalizePath("../empirical/analysis_lm.R"))

stargazer::stargazer(m_alpha$model, m_beta$model, m_gamma$model,
                     header = FALSE,
                     title = "Estimated parameters of robust linear regression models explaining fish species richness in Hokkaido (Japan) and Midwest (US) regions. Dependent variables were log-10 transformed. Environmental variables (air temperature, precipitation, logit \\% forest) are deviations from the regional averages and were standardized to a mean of zero and a standard deviation of one.",
                     type = "latex",
                     ci = TRUE,
                     covariate.labels = c("$log_{10}$ Watershed area",
                                          "$log_{10}$ Branching probability",
                                          "Region (Midwest vs. Hokkaido)",
                                          "Air temperature",
                                          "Precipitation",
                                          "Logit \\% forest",
                                          "Intercept"),
                     single.row = FALSE,
                     digits = 2,
                     dep.var.labels.include = FALSE,
                     column.labels = c("$\\alpha$ richness", "$\\beta$ richness", "$\\gamma$ richness"),
                     keep.stat = c("rsq"),
                     model.numbers = FALSE)

```
